\LARGE\bf \qustop: Quantum state optimizer

### 2021-05-05 docs/paper/main.tex
Adding to tests, examples, and tutorials.

\begin{abstract}
    The \qustop\ package is an open-source Python module for studying various
    quantum state optimization scenarios including calculating optimal values
    for quantum state distinguishability, quantum state exclusion, and quantum
    state cloning.
\end{abstract}

@@

@@

@@

\subsubsection*{Example: Indistinguishable maximally entangled states}

\subsubsection*{Example: Entanglement cost of distinguishing Bell states}

>>>>

\begin{abstract}
    The \qustop\ package is an open-source Python module for studying various
    quantum state optimization scenarios including calculating optimal values
    for quantum state distinguishability, quantum state exclusion, and quantum
    state cloning. We showcase how \qustop \ can be used to verify known results
    in the domain of quantum state distinguishability as well as how it can be
    used as a numerical utility for new results. The \qustop \ package is
    publicly accessible on GitHub at~\cite{}.
\end{abstract}

@@

We assume the reader is familiar with the notions of quantum information as
contained in~\cite{nielsen2002quantum} and~\cite{wilde2013quantum}. We will
make use of the notation and terminology found in~\cite{watrous2018theory}.

Let $\X = \complex^N$ denote a finite-dimensional complex Euclidean space with
a fixed standard basis $\{\ket{1}, \ldots, \ket{N} \}$ for some positive
integer $N$. We use sets $\Lin(\X), \Pos(\X), \Herm(\X), \Density(\X)$, and
$\Unitary(\X)$ to represent the set of a linear operators, positive
semidefinite operators, Hermitian operators, density operators, and unitary
operators acting on the space $\X$.

We begin by describing the setting of quantum state discrimination over an
ensemble of quantum states. In this setting, we are provided with a collection
of tuples (an ensemble)

\begin{equation}
    \{(p_1, \rho_1), \ldots, (p_N, \rho_N) \ \} \subset 
    (\X_1 \otimes \Y_1) \otimes \cdots \otimes (\X_N \otimes \Y_N),
\end{equation}
where $\rho_i \in \Density(\X_i \otimes \Y_i)$ denotes a shared quantum state
between two parties, Alice and Bob, indexed by $i$ and where $p_i$ denotes the
probability with which $\rho_i$ is selected from the ensemble. The state
discrimination procedure involves a random index $k \in \{1, \ldots, N\}$ being
selected. Alice and Bob are then provided with the state $\rho_k$ where their
goal is to determine the index $k$ by performing a measurement on their
respective shared portion of the state.

%------------------------------------------------------------------------------%
\subsubsection*{Quantum states and ensembles}
\label{sec:quantum_states_and_ensembles}
%------------------------------------------------------------------------------%

%------------------------------------------------------------------------------%
\subsubsection*{Semidefinite programming}
\label{sec:semidefinite_programming}
%------------------------------------------------------------------------------%

@@

%------------------------------------------------------------------------------%
\section{Quantum state distinguishability}
\label{sec:qsd}
%------------------------------------------------------------------------------%

%------------------------------------------------------------------------------%
\subsubsection*{Example: Indistinguishable maximally entangled states}
\label{sec:indistinguishable_mes}
%------------------------------------------------------------------------------%

%------------------------------------------------------------------------------%
\subsubsection*{Example: Entanglement cost of distinguishing Bell states}
\label{sec:entanglement_cost_bell}
%------------------------------------------------------------------------------%

@@

%------------------------------------------------------------------------------%
\section{Quantum state exclusion}
\label{sec:qse}
%------------------------------------------------------------------------------%

%------------------------------------------------------------------------------%
\section{Quantum state cloning}
\label{sec:qsc}
%------------------------------------------------------------------------------%
